---
title: "Sample Results Tables for Indian and South African Companies"
author: "OpenAI"
date: "2026-03-12"
output:
  word_document:
    toc: true
  pdf_document:
    latex_engine: xelatex
  html_document:
    toc: true
    number_sections: true
fontsize: 9pt
geometry: margin=1in
mainfont: Palatino Linotype
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{caption}
- \captionsetup[table]{font=small,labelfont=bf,textfont=normalfont}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
options(knitr.kable.NA = "")
kbl <- function(x, caption, align=NULL, longtable=FALSE) {
  if (knitr::is_latex_output()) {
    knitr::kable(x, format = "latex", booktabs = TRUE, longtable = longtable, align = align, caption = caption)
  } else {
    knitr::kable(x, format = "html", align = align, caption = caption)
  }
}
```

```{css, echo=FALSE}
body { font-family: "Palatino Linotype", Palatino, "Book Antiqua", serif; font-size: 9pt; }
table { font-family: "Palatino Linotype", Palatino, "Book Antiqua", serif; font-size: 9pt; width: 100%; border-collapse: collapse; }
th, td { padding-top: 12px; padding-bottom: 12px; }
caption { caption-side: top; text-align: left; font-weight: normal; margin-bottom: 10px; }
```

# Overview

This document provides **illustrative sample tables** for two country groups:

-   **India**: Coromandel, JSW Steel, BASF India, Ambuja Cement, Aarti Industries Limited, GNFC
-   **South Africa**: Kumba Iron Ore, Wesizwe, Gemfields, BHP, AECI, Anglo American

These values are **sample placeholders for manuscript drafting only**. They are **not empirical results** until the pipeline is run on the underlying company reports.

# India

## Table 1. Company-level benchmark and reliability

```{r}
india_benchmark <- data.frame(
  Company = c("Coromandel","JSW Steel","BASF India","Ambuja Cement","Aarti Industries Limited","GNFC"),
  `Retrieval Recall@5` = c(0.78,0.76,0.74,0.77,0.73,0.75),
  `SDG F1` = c(0.81,0.79,0.77,0.80,0.76,0.78),
  `Stage Accuracy` = c(0.72,0.74,0.71,0.75,0.70,0.73),
  `Valid-item Precision` = c(0.88,0.86,0.89,0.87,0.85,0.86),
  `Over-claim Rate` = c(0.12,0.14,0.10,0.11,0.13,0.12),
  check.names = FALSE
)
kbl(india_benchmark, "Company-level benchmark and reliability", align = c("l","r","r","r","r","r"))
```

## Table 2. Company-level substantive disclosure profile

```{r}
india_substantive <- data.frame(
  Company = c("Coromandel","JSW Steel","BASF India","Ambuja Cement","Aarti Industries Limited","GNFC"),
  `Valid Evidence Units` = c(35,41,33,38,31,34),
  `Rhetoric Share` = c(0.26,0.22,0.29,0.24,0.31,0.27),
  `Commitment Share` = c(0.28,0.25,0.30,0.27,0.29,0.29),
  `Implementation Share` = c(0.46,0.53,0.41,0.49,0.40,0.44),
  `Measured Implementation Share` = c(0.26,0.31,0.21,0.29,0.19,0.24),
  `Mean Evidence Score` = c(3.9,4.2,3.7,4.0,3.6,3.8),
  `Dominant SDGs` = c("SDG 2, SDG 12, SDG 13","SDG 8, SDG 9, SDG 12, SDG 13","SDG 6, SDG 12, SDG 13","SDG 9, SDG 11, SDG 12, SDG 13","SDG 6, SDG 8, SDG 12","SDG 2, SDG 6, SDG 12, SDG 13"),
  check.names = FALSE
)
kbl(india_substantive, "Company-level substantive disclosure profile", align = c("l","r","r","r","r","r","r","l"), longtable = TRUE)
```

## Table 3. Longitudinal disclosure trend summary

```{r}
india_longitudinal <- data.frame(
  Company = c("Coromandel","JSW Steel","BASF India","Ambuja Cement","Aarti Industries Limited","GNFC"),
  `Years Covered` = c("2019–2025","2019–2025","2019–2025","2019–2025","2019–2025","2019–2025"),
  `Implementation Trend Slope` = c("+0.05/year","+0.06/year","+0.03/year","+0.05/year","+0.03/year","+0.04/year"),
  `Rhetoric Trend Slope` = c("-0.04/year","-0.03/year","-0.02/year","-0.03/year","-0.01/year","-0.03/year"),
  `Most Persistent SDGs` = c("SDG 2, SDG 12, SDG 13","SDG 8, SDG 9, SDG 12, SDG 13","SDG 6, SDG 12, SDG 13","SDG 9, SDG 11, SDG 12, SDG 13","SDG 6, SDG 8, SDG 12","SDG 2, SDG 6, SDG 12, SDG 13"),
  Interpretation = c("Progressive shift from commitment language to implementation evidence","Strongest improvement in operational and measurable disclosure","Gradual improvement, but more moderate than heavy industry peers","Increasing emphasis on implementation and quantitative evidence","Incremental improvement with persistent policy-heavy language","Moderate transition toward more measurable implementation disclosure"),
  check.names = FALSE
)
kbl(india_longitudinal, "Longitudinal disclosure trend summary", align = c("l","l","l","l","l","l"), longtable = TRUE)
```

# South Africa

## Table 4. Company-level benchmark and reliability

```{r}
sa_benchmark <- data.frame(
  Company = c("Kumba Iron Ore","Wesizwe","Gemfields","BHP","AECI","Anglo American"),
  `Retrieval Recall@5` = c(0.79,0.71,0.74,0.80,0.75,0.82),
  `SDG F1` = c(0.82,0.73,0.77,0.83,0.78,0.84),
  `Stage Accuracy` = c(0.76,0.68,0.72,0.77,0.73,0.79),
  `Valid-item Precision` = c(0.89,0.83,0.86,0.90,0.87,0.91),
  `Over-claim Rate` = c(0.10,0.16,0.13,0.09,0.11,0.08),
  check.names = FALSE
)
kbl(sa_benchmark, "Company-level benchmark and reliability", align = c("l","r","r","r","r","r"))
```

## Table 5. Company-level substantive disclosure profile

```{r}
sa_substantive <- data.frame(
  Company = c("Kumba Iron Ore","Wesizwe","Gemfields","BHP","AECI","Anglo American"),
  `Valid Evidence Units` = c(39,24,29,44,32,47),
  `Rhetoric Share` = c(0.21,0.35,0.28,0.19,0.27,0.18),
  `Commitment Share` = c(0.24,0.29,0.27,0.23,0.28,0.22),
  `Implementation Share` = c(0.55,0.36,0.45,0.58,0.45,0.60),
  `Measured Implementation Share` = c(0.33,0.15,0.24,0.36,0.25,0.39),
  `Mean Evidence Score` = c(4.3,3.3,3.8,4.4,3.9,4.6),
  `Dominant SDGs` = c("SDG 8, SDG 9, SDG 12, SDG 13","SDG 8, SDG 9, SDG 13","SDG 5, SDG 8, SDG 12, SDG 15","SDG 8, SDG 12, SDG 13, SDG 15","SDG 6, SDG 8, SDG 12, SDG 13","SDG 8, SDG 12, SDG 13, SDG 15"),
  check.names = FALSE
)
kbl(sa_substantive, "Company-level substantive disclosure profile", align = c("l","r","r","r","r","r","r","l"), longtable = TRUE)
```

## Table 6. Longitudinal disclosure trend summary

```{r}
sa_longitudinal <- data.frame(
  Company = c("Kumba Iron Ore","Wesizwe","Gemfields","BHP","AECI","Anglo American"),
  `Years Covered` = c("2019–2025","2019–2025","2019–2025","2019–2025","2019–2025","2019–2025"),
  `Implementation Trend Slope` = c("+0.06/year","+0.02/year","+0.04/year","+0.06/year","+0.04/year","+0.07/year"),
  `Rhetoric Trend Slope` = c("-0.03/year","-0.01/year","-0.02/year","-0.03/year","-0.02/year","-0.04/year"),
  `Most Persistent SDGs` = c("SDG 8, SDG 9, SDG 12, SDG 13","SDG 8, SDG 9, SDG 13","SDG 5, SDG 8, SDG 12, SDG 15","SDG 8, SDG 12, SDG 13, SDG 15","SDG 6, SDG 8, SDG 12, SDG 13","SDG 8, SDG 12, SDG 13, SDG 15"),
  Interpretation = c("Steady rise in operational and climate-related disclosure","Limited but positive improvement from lower disclosure maturity baseline","Moderate shift toward more implementation and community evidence","Strong and sustained measurable implementation pattern","Progressive strengthening of production, safety, and climate disclosure","Strongest disclosure maturity and broadest SDG persistence in the group"),
  check.names = FALSE
)
kbl(sa_longitudinal, "Longitudinal disclosure trend summary", align = c("l","l","l","l","l","l"), longtable = TRUE)
```

# Cross-country portfolio summary

## Table 7. Country-level portfolio summary

```{r}
country_summary <- data.frame(
  Group = c("India","South Africa"),
  Companies = c(6,6),
  `Average Retrieval Recall@5` = c(0.76,0.77),
  `Average SDG F1` = c(0.79,0.80),
  `Average Stage Accuracy` = c(0.73,0.74),
  `Average Valid-item Precision` = c(0.87,0.88),
  `Average Over-claim Rate` = c(0.12,0.11),
  `Mean Rhetoric Share` = c(0.27,0.25),
  `Mean Commitment Share` = c(0.28,0.26),
  `Mean Implementation Share` = c(0.46,0.50),
  `Mean Measured Implementation Share` = c(0.25,0.29),
  `Most Frequent Dominant SDGs` = c("SDG 12, SDG 13","SDG 8, SDG 12, SDG 13"),
  check.names = FALSE
)
kbl(country_summary, "Country-level portfolio summary", align = c("l","r","r","r","r","r","r","r","r","r","l"))
```

# Sample narrative paragraph

Across the illustrative two-country sample, benchmark performance was broadly consistent, with South African firms showing slightly higher mean implementation share and measured implementation share than Indian firms. Within the South African group, Anglo American and BHP displayed the strongest sample implementation-oriented profiles, while Kumba Iron Ore also showed a relatively mature disclosure pattern. Within the Indian group, JSW Steel and Ambuja Cement showed the strongest implementation shares, while Coromandel and GNFC displayed stronger agriculture- and production-linked SDG patterns. These results are included only as manuscript-format examples and should not be interpreted as empirical findings until the underlying report set has been processed and validated.

# Important note

These tables are **illustrative sample numbers only**. They are suitable for: - structuring a manuscript - matching a table style and layout - drafting comparative results text

They are **not real results** until the pipeline is run on each company’s report set.
