---
title: "Model and Performance Plots for SDG Disclosure Analysis"
author: "OpenAI"
date: "2026-03-12"
output:
  html_document:
    toc: true
    number_sections: true
    df_print: paged
  word_document: default
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(tidyverse)
library(jsonlite)
library(scales)
library(patchwork)
library(viridis)

theme_set(
  theme_minimal(base_family = "Palatino Linotype", base_size = 9) +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank(),
      plot.title = element_text(face = "bold"),
      axis.title = element_text(face = "bold"),
      strip.text = element_text(face = "bold")
    )
)
```

# Overview

This R Markdown file provides a **publication-oriented plotting
template** for the SDG disclosure workflow.

It includes templates for: - retrieval performance - over-claim rate by
model - ablation analysis - SDG coverage heatmap - disclosure maturity
profile by company - implementation share over time - rhetoric share
over time - cross-model agreement heatmap

These values are **illustrative sample data** for layout and workflow
demonstration. Replace them with your actual outputs when available.

# Data input

You can either: 1. replace the sample tables below with real data
frames, or 2. load JSON/CSV outputs from your pipeline.

## Optional: load real data

```{r eval=FALSE}
# Example for JSON
evidence <- jsonlite::fromJSON("evidence.json", flatten = TRUE)

# Example for CSV
performance_df <- readr::read_csv("performance_summary.csv")
longitudinal_df <- readr::read_csv("longitudinal_summary.csv")
agreement_df <- readr::read_csv("cross_model_agreement.csv")
```

# Sample data

```{r}
companies <- c(
  "Coromandel","JSW Steel","BASF India","Ambuja Cement","Aarti Industries Limited","GNFC",
  "Kumba Iron Ore","Wesizwe","Gemfields","BHP","AECI","Anglo American"
)

country_map <- tibble(
  Company = companies,
  Country = c(rep("India", 6), rep("South Africa", 6))
)

# Retrieval performance sample
recall_df <- expand_grid(
  Model = c("Mistral", "Gemma2", "Llama3"),
  k = c(1, 3, 5, 10)
) |>
  mutate(
    Recall = case_when(
      Model == "Mistral" & k == 1 ~ 0.42,
      Model == "Mistral" & k == 3 ~ 0.66,
      Model == "Mistral" & k == 5 ~ 0.78,
      Model == "Mistral" & k == 10 ~ 0.89,
      Model == "Gemma2" & k == 1 ~ 0.40,
      Model == "Gemma2" & k == 3 ~ 0.64,
      Model == "Gemma2" & k == 5 ~ 0.74,
      Model == "Gemma2" & k == 10 ~ 0.85,
      TRUE ~ c(0.39,0.61,0.72,0.82)
    )
  )

# Over-claim rate sample
overclaim_df <- tibble(
  Model = c("Mistral", "Gemma2", "Llama3"),
  `Over-claim Rate` = c(0.12, 0.08, 0.15)
)

# Ablation study sample
ablation_df <- tribble(
  ~Variant, ~Metric, ~Value,
  "Full system", "SDG F1", 0.81,
  "No validation", "SDG F1", 0.80,
  "No hybrid retrieval", "SDG F1", 0.71,
  "No section-aware chunking", "SDG F1", 0.74,
  "Single-prompt baseline", "SDG F1", 0.62,
  "Full system", "Stage Accuracy", 0.72,
  "No validation", "Stage Accuracy", 0.71,
  "No hybrid retrieval", "Stage Accuracy", 0.66,
  "No section-aware chunking", "Stage Accuracy", 0.68,
  "Single-prompt baseline", "Stage Accuracy", 0.55,
  "Full system", "Over-claim Rate", 0.12,
  "No validation", "Over-claim Rate", 0.27,
  "No hybrid retrieval", "Over-claim Rate", 0.15,
  "No section-aware chunking", "Over-claim Rate", 0.17,
  "Single-prompt baseline", "Over-claim Rate", 0.34
)

# SDG coverage heatmap sample
sdg_heatmap_df <- expand_grid(
  Company = companies,
  SDG = c("SDG 2","SDG 5","SDG 6","SDG 8","SDG 9","SDG 11","SDG 12","SDG 13","SDG 15")
) |>
  mutate(
    Score = sample(c(0, 1, 2, 3, 4, 5), n(), replace = TRUE,
                   prob = c(0.18, 0.12, 0.15, 0.20, 0.18, 0.17))
  ) |>
  left_join(country_map, by = "Company")

# Disclosure maturity profile sample
maturity_df <- tribble(
  ~Company, ~Rhetoric, ~Commitment, ~Implementation, ~Measured,
  "Coromandel", 0.26, 0.28, 0.20, 0.26,
  "JSW Steel", 0.22, 0.25, 0.22, 0.31,
  "BASF India", 0.29, 0.30, 0.20, 0.21,
  "Ambuja Cement", 0.24, 0.27, 0.20, 0.29,
  "Aarti Industries Limited", 0.31, 0.29, 0.21, 0.19,
  "GNFC", 0.27, 0.29, 0.20, 0.24,
  "Kumba Iron Ore", 0.21, 0.24, 0.22, 0.33,
  "Wesizwe", 0.35, 0.29, 0.21, 0.15,
  "Gemfields", 0.28, 0.27, 0.21, 0.24,
  "BHP", 0.19, 0.23, 0.22, 0.36,
  "AECI", 0.27, 0.28, 0.20, 0.25,
  "Anglo American", 0.18, 0.22, 0.21, 0.39
) |>
  pivot_longer(cols = -Company, names_to = "Category", values_to = "Share") |>
  left_join(country_map, by = "Company")

# Longitudinal sample
years <- 2019:2025
longitudinal_df <- expand_grid(
  Company = companies,
  Year = years
) |>
  left_join(country_map, by = "Company") |>
  mutate(
    ImplementationShare = case_when(
      Company == "Anglo American" ~ seq(0.32, 0.60, length.out = length(years)),
      Company == "BHP" ~ seq(0.34, 0.58, length.out = length(years)),
      Company == "JSW Steel" ~ seq(0.28, 0.53, length.out = length(years)),
      Company == "Ambuja Cement" ~ seq(0.30, 0.49, length.out = length(years)),
      TRUE ~ seq(0.22, 0.45, length.out = length(years))
    ),
    RhetoricShare = case_when(
      Company == "Anglo American" ~ seq(0.38, 0.18, length.out = length(years)),
      Company == "BHP" ~ seq(0.35, 0.19, length.out = length(years)),
      Company == "JSW Steel" ~ seq(0.34, 0.22, length.out = length(years)),
      Company == "Ambuja Cement" ~ seq(0.33, 0.24, length.out = length(years)),
      TRUE ~ seq(0.40, 0.27, length.out = length(years))
    )
  )

# Cross-model agreement sample
agreement_df <- tibble(
  Company = companies,
  `SDG Agreement` = c(0.82,0.79,0.84,0.81,0.77,0.80,0.83,0.74,0.79,0.85,0.80,0.87),
  `Stage Agreement` = c(0.76,0.74,0.78,0.77,0.72,0.75,0.78,0.69,0.73,0.80,0.75,0.82),
  `Over-claim Difference` = c(0.04,0.06,0.03,0.04,0.05,0.04,0.03,0.07,0.05,0.03,0.04,0.02)
) |>
  left_join(country_map, by = "Company") |>
  pivot_longer(cols = c(`SDG Agreement`, `Stage Agreement`, `Over-claim Difference`),
               names_to = "Metric", values_to = "Value")
```

# Figure 1. Retrieval performance

```{r}
ggplot(recall_df, aes(x = k, y = Recall, color = Model)) +
  geom_line(linewidth = 0.7) +
  geom_point(size = 1.8) +
  scale_x_continuous(breaks = c(1, 3, 5, 10)) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(
    title = "Figure 1. Retrieval performance across top-k thresholds",
    x = "Top-k",
    y = "Recall"
  )
```

# Figure 2. Over-claim rate by model

```{r}
ggplot(overclaim_df, aes(x = Model, y = `Over-claim Rate`, fill = Model)) +
  geom_col(width = 0.65, show.legend = FALSE) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 0.4)) +
  labs(
    title = "Figure 2. Over-claim rate by model",
    x = NULL,
    y = "Over-claim rate"
  )
```

# Figure 3. Ablation analysis

```{r}
ggplot(ablation_df, aes(x = Variant, y = Value, fill = Variant)) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~Metric, scales = "free_y", ncol = 1) +
  coord_flip() +
  labs(
    title = "Figure 3. Ablation analysis",
    x = NULL,
    y = "Metric value"
  )
```

# Figure 4. SDG coverage heatmap

```{r}
ggplot(sdg_heatmap_df, aes(x = SDG, y = fct_rev(Company), fill = Score)) +
  geom_tile(color = "white", linewidth = 0.2) +
  facet_wrap(~Country, scales = "free_y", ncol = 1) +
  scale_fill_viridis(name = "Coverage / score", option = "C") +
  labs(
    title = "Figure 4. SDG coverage heatmap by company",
    x = NULL,
    y = NULL
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Figure 5. Disclosure maturity profile by company

```{r}
ggplot(maturity_df, aes(x = Company, y = Share, fill = Category)) +
  geom_col() +
  facet_wrap(~Country, scales = "free_x", ncol = 1) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(
    title = "Figure 5. Disclosure maturity profile by company",
    x = NULL,
    y = "Share of valid evidence units"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

# Figure 6. Implementation share over time

```{r}
ggplot(longitudinal_df, aes(x = Year, y = ImplementationShare, color = Company)) +
  geom_line(linewidth = 0.7) +
  facet_wrap(~Country, ncol = 1) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 0.7)) +
  labs(
    title = "Figure 6. Implementation share over time",
    x = NULL,
    y = "Implementation share"
  ) +
  theme(legend.position = "none")
```

# Figure 7. Rhetoric share over time

```{r}
ggplot(longitudinal_df, aes(x = Year, y = RhetoricShare, color = Company)) +
  geom_line(linewidth = 0.7) +
  facet_wrap(~Country, ncol = 1) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 0.5)) +
  labs(
    title = "Figure 7. Rhetoric share over time",
    x = NULL,
    y = "Rhetoric share"
  ) +
  theme(legend.position = "none")
```

# Figure 8. Cross-model agreement heatmap

```{r}
ggplot(agreement_df, aes(x = Metric, y = fct_rev(Company), fill = Value)) +
  geom_tile(color = "white", linewidth = 0.2) +
  facet_wrap(~Country, scales = "free_y", ncol = 1) +
  scale_fill_viridis(name = "Value", option = "D") +
  labs(
    title = "Figure 8. Cross-model agreement heatmap",
    x = NULL,
    y = NULL
  ) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

# Combined main-paper figure options

```{r}
p1 <- ggplot(recall_df, aes(x = k, y = Recall, color = Model)) +
  geom_line(linewidth = 0.7) +
  geom_point(size = 1.6) +
  scale_x_continuous(breaks = c(1, 3, 5, 10)) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(title = "A. Retrieval performance", x = "Top-k", y = "Recall")

p2 <- ggplot(overclaim_df, aes(x = Model, y = `Over-claim Rate`, fill = Model)) +
  geom_col(width = 0.65, show.legend = FALSE) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 0.4)) +
  labs(title = "B. Over-claim rate", x = NULL, y = "Rate")

p3 <- ggplot(maturity_df, aes(x = Company, y = Share, fill = Category)) +
  geom_col() +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(title = "C. Disclosure maturity", x = NULL, y = "Share") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1), legend.position = "none")

p4 <- ggplot(agreement_df, aes(x = Metric, y = fct_rev(Company), fill = Value)) +
  geom_tile(color = "white", linewidth = 0.2) +
  scale_fill_viridis(option = "D") +
  labs(title = "D. Cross-model agreement", x = NULL, y = NULL) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1), legend.position = "none")

(p1 | p2) / (p3 | p4)
```

# Notes

-   Replace the sample data frames with actual outputs from your
    pipeline.
-   If you want company-specific or country-specific figures only,
    subset the data frames before plotting.
-   If you want confidence calibration plots, first make sure the
    confidence field is populated consistently in your extraction
    output.
-   Some earlier uploaded files in this chat have expired, so this
    template does not automatically load previous report outputs.
