---
title: "Publishable Tables with rempsyc for India and South Africa"
author: "OpenAI"
date: "2026-03-12"
output:
  word_document: default
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(rempsyc)
library(flextable)

theme_publishable <- function(ft) {
  ft |>
    font(fontname = "Palatino Linotype", part = "all") |>
    fontsize(size = 9, part = "all") |>
    line_spacing(space = 1.0, part = "all") |>
    padding(padding.top = 4, padding.bottom = 4, part = "all") |>
    align(align = "left", part = "header") |>
    autofit()
}
```

# Overview

This document uses `rempsyc::nice_table()` to create publication-ready tables, following the package workflow for APA-style tables and Word export. The values below are illustrative placeholders, not empirical results.

# India

## Table 1. Company-level benchmark and reliability

```{r}
india_benchmark <- data.frame(
  Company = c("Coromandel", "JSW Steel", "BASF India", "Ambuja Cement", "Aarti Industries Limited", "GNFC"),
  `Retrieval Recall@5` = c(0.78, 0.76, 0.74, 0.77, 0.73, 0.75),
  `SDG F1` = c(0.81, 0.79, 0.77, 0.80, 0.76, 0.78),
  `Stage Accuracy` = c(0.72, 0.74, 0.71, 0.75, 0.70, 0.73),
  `Valid-item Precision` = c(0.88, 0.86, 0.89, 0.87, 0.85, 0.86),
  `Over-claim Rate` = c(0.12, 0.14, 0.10, 0.11, 0.13, 0.12),
  check.names = FALSE
)

ft_india_benchmark <- nice_table(
  india_benchmark,
  title = c("Table 1", "Company-level benchmark and reliability (India)"),
  note = c("Illustrative values only.", "Not empirical results.")
) |>
  theme_publishable()

ft_india_benchmark
```

## Table 2. Company-level substantive disclosure profile

```{r}
india_substantive <- data.frame(
  Company = c("Coromandel", "JSW Steel", "BASF India", "Ambuja Cement", "Aarti Industries Limited", "GNFC"),
  `Valid Evidence Units` = c(35, 41, 33, 38, 31, 34),
  `Rhetoric Share` = c(0.26, 0.22, 0.29, 0.24, 0.31, 0.27),
  `Commitment Share` = c(0.28, 0.25, 0.30, 0.27, 0.29, 0.29),
  `Implementation Share` = c(0.46, 0.53, 0.41, 0.49, 0.40, 0.44),
  `Measured Implementation Share` = c(0.26, 0.31, 0.21, 0.29, 0.19, 0.24),
  `Mean Evidence Score` = c(3.9, 4.2, 3.7, 4.0, 3.6, 3.8),
  `Dominant SDGs` = c(
    "SDG 2, SDG 12, SDG 13",
    "SDG 8, SDG 9, SDG 12, SDG 13",
    "SDG 6, SDG 12, SDG 13",
    "SDG 9, SDG 11, SDG 12, SDG 13",
    "SDG 6, SDG 8, SDG 12",
    "SDG 2, SDG 6, SDG 12, SDG 13"
  ),
  check.names = FALSE
)

ft_india_substantive <- nice_table(
  india_substantive,
  title = c("Table 2", "Company-level substantive disclosure profile (India)"),
  note = c("Illustrative values only.", "Not empirical results.")
) |>
  theme_publishable()

ft_india_substantive
```

# South Africa

## Table 3. Company-level benchmark and reliability

```{r}
sa_benchmark <- data.frame(
  Company = c("Kumba Iron Ore", "Wesizwe", "Gemfields", "BHP", "AECI", "Anglo American"),
  `Retrieval Recall@5` = c(0.79, 0.71, 0.74, 0.80, 0.75, 0.82),
  `SDG F1` = c(0.82, 0.73, 0.77, 0.83, 0.78, 0.84),
  `Stage Accuracy` = c(0.76, 0.68, 0.72, 0.77, 0.73, 0.79),
  `Valid-item Precision` = c(0.89, 0.83, 0.86, 0.90, 0.87, 0.91),
  `Over-claim Rate` = c(0.10, 0.16, 0.13, 0.09, 0.11, 0.08),
  check.names = FALSE
)

ft_sa_benchmark <- nice_table(
  sa_benchmark,
  title = c("Table 3", "Company-level benchmark and reliability (South Africa)"),
  note = c("Illustrative values only.", "Not empirical results.")
) |>
  theme_publishable()

ft_sa_benchmark
```

## Table 4. Company-level substantive disclosure profile

```{r}
sa_substantive <- data.frame(
  Company = c("Kumba Iron Ore", "Wesizwe", "Gemfields", "BHP", "AECI", "Anglo American"),
  `Valid Evidence Units` = c(39, 24, 29, 44, 32, 47),
  `Rhetoric Share` = c(0.21, 0.35, 0.28, 0.19, 0.27, 0.18),
  `Commitment Share` = c(0.24, 0.29, 0.27, 0.23, 0.28, 0.22),
  `Implementation Share` = c(0.55, 0.36, 0.45, 0.58, 0.45, 0.60),
  `Measured Implementation Share` = c(0.33, 0.15, 0.24, 0.36, 0.25, 0.39),
  `Mean Evidence Score` = c(4.3, 3.3, 3.8, 4.4, 3.9, 4.6),
  `Dominant SDGs` = c(
    "SDG 8, SDG 9, SDG 12, SDG 13",
    "SDG 8, SDG 9, SDG 13",
    "SDG 5, SDG 8, SDG 12, SDG 15",
    "SDG 8, SDG 12, SDG 13, SDG 15",
    "SDG 6, SDG 8, SDG 12, SDG 13",
    "SDG 8, SDG 12, SDG 13, SDG 15"
  ),
  check.names = FALSE
)

ft_sa_substantive <- nice_table(
  sa_substantive,
  title = c("Table 4", "Company-level substantive disclosure profile (South Africa)"),
  note = c("Illustrative values only.", "Not empirical results.")
) |>
  theme_publishable()

ft_sa_substantive
```

# Save tables to Word

```{r eval=FALSE}
# Example: save one table to Word
flextable::save_as_docx(ft_india_benchmark, path = "table_india_benchmark.docx")

# Example: save multiple tables to one Word file
flextable::save_as_docx(
  `Table 1` = ft_india_benchmark,
  `Table 2` = ft_india_substantive,
  `Table 3` = ft_sa_benchmark,
  `Table 4` = ft_sa_substantive,
  path = "publishable_tables_india_south_africa.docx"
)
```

# Notes

- `rempsyc::nice_table()` is used as the base table generator.
- `flextable` formatting is applied afterward to match the requested manuscript style more closely:
  - font: Palatino Linotype
  - size: 9 pt
- These are sample values for layout and drafting only.
