---
title: "Methods and Validation"
---

```{r setup, include=FALSE}
library(here); library(reactable); library(gt); library(plotly)
source(here("R", "load_evidence.R"))
source(here("R", "plot_themes.R"))
source(here("R", "scoring_helpers.R"))
```

## Pipeline overview

The extraction pipeline is a linear LangGraph workflow with eight deterministic nodes. No unconstrained agents; the LLM is used only for extraction and normalization.

```{mermaid}
flowchart LR
    A([PDF input]) --> B[ingest_pdf]
    B --> C[chunk_document]
    C --> D[retrieve_candidate_chunks]
    D --> E[extract_evidence]
    E --> F[validate_evidence]
    F --> G[score_evidence]
    G --> H[aggregate_findings]
    H --> I([JSON · CSV · MD outputs])

    style B fill:#19486A,color:#fff
    style C fill:#19486A,color:#fff
    style D fill:#0A97D9,color:#fff
    style E fill:#FCC30B,color:#000
    style F fill:#E5243B,color:#fff
    style G fill:#3F7E44,color:#fff
    style H fill:#3F7E44,color:#fff
```

**Key design decisions:**

- The LLM assigns `candidate_sdgs`, `evidence_tags`, `implementation_stage`, and confidence — all normalization tasks
- Validation, scoring, and final strength assessment are **deterministic Python** — the model cannot inflate ratings
- Conservative extraction: when uncertain, the model is instructed to return no evidence rather than a speculative item

---

## Scoring rubric

The `computed_score` (0–13) is calculated from four additive components. The model is never asked to assign weak/moderate/strong directly.

```{r scoring-table}
tibble(
  Component    = c(
    "A. Action maturity — mention_only",
    "A. Action maturity — planned_action",
    "A. Action maturity — implementation_in_progress",
    "A. Action maturity — implemented_with_measurable_evidence",
    "B. Tag bonus — policy",
    "B. Tag bonus — initiative",
    "B. Tag bonus — target",
    "B. Tag bonus — kpi",
    "B. Tag bonus — measured_outcome",
    "C. Support — quantitative_support",
    "C. Support — oversight_support"
  ),
  Points = c(1, 2, 3, 4, 1, 1, 1, 1, 2, 1, 1),
  Notes  = c(
    "SDG is mentioned without any action language",
    "Stated plans or commitments exist",
    "Active implementation underway",
    "Outcomes are measured and reported",
    "+1 if evidence references a policy",
    "+1 if a specific initiative is named",
    "+1 if a target is stated",
    "+1 if a KPI is tracked",
    "+2 if a measured outcome is present (e.g., numbers, percentages)",
    "+1 if numeric or metric-like evidence is present",
    "+1 if board, committee, or executive oversight is explicitly named"
  )
) |>
  gt() |>
  tab_header(title = "Evidence scoring rubric (documented max = 13)") |>
  tab_row_group(label = "Strength thresholds", rows = FALSE) |>
  cols_label(Component = "Component", Points = "Points", Notes = "Notes") |>
  tab_style(
    style = cell_fill(color = "#F0F4F8"),
    locations = cells_body(rows = c(1, 5, 10))
  ) |>
  tab_footnote("Strength: 1–2 = weak · 3–5 = moderate · 6+ = strong") |>
  opt_table_font(font = "monospace", size = 13)
```

---

## Validation rules

Eight deterministic rules must all pass for an evidence item to be retained. Failure causes rejection with the specific rule recorded.

```{r validation-table}
tibble(
  `Rule #` = 1:8,
  Condition = c(
    "page_number > 0",
    "evidence_text is non-empty",
    "candidate_sdgs is non-empty",
    "implementation_stage is in the valid set",
    "all evidence_tags are in the valid set",
    "measured_outcome tag requires quantitative_support = TRUE",
    "governance tag requires oversight_support = TRUE",
    "implemented_with_measurable_evidence requires quantitative_support = TRUE"
  ),
  Rationale = c(
    "Every item must be traceable to a specific page",
    "Evidence must have verbatim or near-verbatim text",
    "At least one SDG must be identified",
    "Stage must be one of four defined values",
    "Tags must be one of seven defined values",
    "Cannot claim measured outcomes without numbers",
    "Cannot claim governance without naming the oversight body",
    "Cannot claim measurable implementation without numeric evidence"
  )
) |>
  reactable(
    columns = list(
      `Rule #`   = colDef(maxWidth = 65, align = "center"),
      Condition  = colDef(minWidth = 220),
      Rationale  = colDef(minWidth = 280)
    ),
    striped = TRUE, highlight = TRUE, compact = TRUE,
    defaultPageSize = 8
  )
```

---

## Extraction quality audit

For each report: how many chunks were retrieved, how many evidence items extracted, how many passed validation.

```{r quality-audit}
audit <- run_meta |>
  arrange(report_year) |>
  mutate(
    pass_rate = scales::percent(n_valid / (n_valid + n_rejected), accuracy = 1)
  ) |>
  select(
    Year       = report_year,
    Report     = report_name,
    Valid      = n_valid,
    Rejected   = n_rejected,
    `Pass rate` = pass_rate,
    Assessment  = overall_assessment
  )

reactable(
  audit,
  columns = list(
    Year       = colDef(maxWidth = 60, align = "center"),
    Valid      = colDef(maxWidth = 70, align = "center",
                        style = function(v) list(color = "#3F7E44", fontWeight = "bold")),
    Rejected   = colDef(maxWidth = 80, align = "center",
                        style = function(v) list(color = "#E5243B")),
    `Pass rate` = colDef(maxWidth = 90, align = "center"),
    Assessment  = colDef(minWidth = 200)
  ),
  striped = TRUE, highlight = TRUE, compact = TRUE
)
```

---

## Construct validity checks

### 1. Does model confidence correlate with computed score?

Higher model-reported confidence should correlate with higher deterministic scores if the model's self-assessment is calibrated.

```{r confidence-score}
p <- ev_wide |>
  ggplot(aes(x = confidence, y = computed_score, colour = computed_strength)) +
  geom_jitter(alpha = 0.4, width = 0.02, height = 0.1, size = 1.5) +
  geom_smooth(method = "lm", se = TRUE, colour = "#19486A", linewidth = 0.8) +
  scale_colour_strength() +
  scale_y_continuous(breaks = 0:13) +
  labs(
    title    = "Model confidence vs. deterministic computed score",
    subtitle = "Each point is one evidence item. Colour = assigned strength.",
    x = "Model-reported confidence [0–1]",
    y = "Computed score [0–13]",
    colour = "Strength"
  )

ggplotly(p)
```

### 2. Tag–stage coherence

Do higher-maturity tags co-occur with higher implementation stages? A `measured_outcome` tag with a `mention_only` stage would be incoherent.

```{r tag-stage-heatmap}
ev |>
  unnest(evidence_tags) |>
  rename(tag = evidence_tags) |>
  count(tag, implementation_stage) |>
  mutate(implementation_stage = factor(
    implementation_stage,
    levels = c("mention_only","planned_action",
               "implementation_in_progress",
               "implemented_with_measurable_evidence")
  )) |>
  ggplot(aes(x = tag, y = implementation_stage, fill = n)) +
  geom_tile(colour = "white") +
  geom_text(aes(label = n), size = 3, colour = "white") +
  scale_fill_gradient(low = "#D9EAD3", high = "#19486A", name = "Count") +
  scale_y_discrete(labels = c(
    "mention_only"                         = "Mention only",
    "planned_action"                       = "Planned action",
    "implementation_in_progress"           = "In progress",
    "implemented_with_measurable_evidence" = "Measurable evidence"
  )) +
  labs(
    title = "Evidence tag × implementation stage co-occurrence",
    subtitle = "Well-calibrated: 'measured_outcome' should appear mainly in higher stages",
    x = "Evidence tag", y = "Implementation stage"
  ) +
  theme_sdg() +
  theme(axis.text.x = element_text(angle = 35, hjust = 1))
```

---

## Known limitations

::: {.callout-warning}
**Retrieval ceiling:** `top_k = 20` chunks per report. Evidence in unchosen chunks is not extracted. Raising top_k increases recall but also extraction time (approximately 4 minutes per chunk on CPU with Gemma2).

**Early reports (2016–2019):** Shorter, less structured PDFs. Section headings were less consistently detected. Comparisons across the full decade should account for this.

**Single model:** All reports were extracted with Gemma2 (Ollama). No inter-model reliability check has been performed. Model comparison is deferred to Phase 2.

**Chunk boundary effects:** Evidence spanning two chunks may be split. The chunker uses 80-token overlap to mitigate this, but some cross-boundary items may be missed or duplicated.
:::
