---
title: "Cross-Company Comparison"
subtitle: "Multi-company SDG disclosure benchmarking"
---

```{r setup, include=FALSE}
library(here); library(reactable); library(plotly); library(gt)
source(here("R", "load_evidence.R"))
source(here("R", "plot_themes.R"))
source(here("R", "scoring_helpers.R"))
source(here("R", "download_helpers.R"))
```

::: {.callout-note}
**Status: Single-company mode.**
This chapter is structured to accommodate multiple companies. To add a new company:

1. Run the Python pipeline on the company's PDF reports
2. Add the company slug to `COMPANIES` in `R/load_evidence.R`
3. Re-render the book (`quarto render`)

All charts and tables below will auto-update with peer data.
:::

```{r company-check}
n_companies <- n_distinct(ev$company)
companies   <- unique(ev$company)
```

## Companies in dataset

```{r companies-table}
run_meta |>
  group_by(company) |>
  summarise(
    Years        = paste(range(report_year), collapse = "–"),
    `N reports`  = n(),
    `Valid items` = sum(n_valid),
    `Avg score`  = round(mean(
      ev_wide |> filter(company == first(company)) |> pull(computed_score),
      na.rm = TRUE
    ), 2),
    .groups = "drop"
  ) |>
  gt() |>
  tab_header(title = "Companies with processed reports") |>
  cols_label(company = "Company")
```

---

## SDG Portfolio Comparison

When multiple companies are loaded, this heatmap shows each company's SDG coverage side by side. Currently showing Coromandel only.

```{r portfolio-comparison}
sdg_company <- ev |>
  group_by(company, sdg) |>
  summarise(
    avg_score = mean(computed_score, na.rm = TRUE),
    n         = n(),
    .groups   = "drop"
  )

p <- sdg_company |>
  ggplot(aes(x = company, y = sdg,
             fill = avg_score,
             text = paste0(company, " · ", sdg,
                           "\nEvidence: ", n,
                           "\nAvg score: ", round(avg_score, 2)))) +
  geom_tile(colour = "white", linewidth = 0.5) +
  geom_text(aes(label = n), colour = "white", size = 3, fontface = "bold") +
  scale_fill_gradient2(
    low = "#D9EAD3", mid = "#4C9F38", high = "#19486A",
    midpoint = 5, na.value = "grey92",
    name = "Avg score"
  ) +
  labs(
    title    = "SDG portfolio comparison across companies",
    subtitle = "Cell colour = average score · Number = evidence count",
    x = NULL, y = NULL
  ) +
  theme_sdg() +
  theme(panel.grid = element_blank(),
        axis.text.y = element_text(size = 9))

ggplotly(p, tooltip = "text") |>
  layout(yaxis = list(autorange = "reversed"))
```

---

## Maturity Benchmarking

```{r maturity-bench}
maturity_all <- compute_maturity_index(ev_wide) |>
  mutate(report_year = as.integer(report_year))

# One trace per company
companies_list <- unique(maturity_all$company)
p <- plot_ly()
for (co in companies_list) {
  d <- maturity_all |> filter(company == co)
  p <- p |>
    add_trace(data = d, x = ~report_year, y = ~maturity_index,
              name = co, type = "scatter", mode = "lines+markers",
              line = list(width = 2), marker = list(size = 7))
}
p |> layout(
  title = "SDG disclosure maturity index by company",
  xaxis = list(title = "Report year",
               tickvals = unique(maturity_all$report_year)),
  yaxis = list(title = "Maturity index [0–1]", range = c(0, 1),
               tickformat = ".0%"),
  legend = list(orientation = "h")
)
```

---

## Implementation Stage Comparison

```{r stage-comparison}
stage_company <- ev_wide |>
  count(company, implementation_stage) |>
  group_by(company) |>
  mutate(pct = n / sum(n)) |>
  ungroup()

p <- stage_company |>
  ggplot(aes(x = company, y = pct,
             fill = implementation_stage,
             text = paste0(STAGE_LABELS[as.character(implementation_stage)],
                           ": ", scales::percent(pct, accuracy = 1)))) +
  geom_col(position = "stack", width = 0.5) +
  scale_fill_stage() +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "Implementation stage composition by company",
    subtitle = "Dark = higher maturity",
    x = NULL, y = "Proportion of evidence items",
    fill = "Stage"
  ) +
  theme_sdg()

ggplotly(p, tooltip = "text")
```

---

## Evidence Quality Comparison

```{r quality-comparison}
quality_company <- ev_wide |>
  group_by(company) |>
  summarise(
    `Avg score`            = round(mean(computed_score, na.rm = TRUE), 2),
    `% Strong`             = scales::percent(mean(computed_strength == "strong", na.rm = TRUE), accuracy = 1),
    `Quantitative support` = scales::percent(mean(quantitative_support, na.rm = TRUE), accuracy = 1),
    `Oversight support`    = scales::percent(mean(oversight_support,    na.rm = TRUE), accuracy = 1),
    `Rejection rate`       = scales::percent(
      nrow(ev_rej[ev_rej$company == first(company), ]) /
      (n() + nrow(ev_rej[ev_rej$company == first(company), ])),
      accuracy = 1
    ),
    .groups = "drop"
  )

make_download_bar(quality_company, "comparison_quality")
reactable(
  quality_company,
  columns = list(
    company = colDef(name = "Company", minWidth = 120)
  ),
  striped = TRUE, highlight = TRUE
)
```

---

## SDG Leadership Rankings

For each SDG, which company has the highest average evidence score? (Populated when ≥ 2 companies are available.)

```{r sdg-leadership}
if (n_companies >= 2) {
  sdg_rank <- ev |>
    group_by(sdg, company) |>
    summarise(avg_score = round(mean(computed_score, na.rm = TRUE), 2), n = n(),
              .groups = "drop") |>
    group_by(sdg) |>
    slice_max(avg_score, n = 1) |>
    ungroup()

  make_download_bar(sdg_rank, "comparison_sdg_rankings")
  reactable(sdg_rank,
            columns = list(
              sdg       = colDef(name = "SDG", maxWidth = 80),
              company   = colDef(name = "Leader"),
              avg_score = colDef(name = "Avg score", maxWidth = 100, align = "center",
                                 format = colFormat(digits = 2)),
              n         = colDef(name = "Evidence items", maxWidth = 130, align = "center")
            ),
            striped = TRUE, highlight = TRUE)
} else {
  cat("SDG leadership rankings require at least 2 companies. Add a second company to unlock this view.")
}
```
