---
title: "Longitudinal Theory Testing"
subtitle: "SDG disclosure as a relational network — maturity transition analysis"
---

```{r setup, include=FALSE}
library(here); library(reactable); library(plotly)
library(ggraph); library(tidygraph); library(visNetwork)
source(here("R", "load_evidence.R"))
source(here("R", "plot_themes.R"))
source(here("R", "scoring_helpers.R"))
source(here("R", "network_helpers.R"))

co_ev      <- ev      |> filter(company == "coromandel")
co_ev_wide <- ev_wide |> filter(company == "coromandel")
co_sdg_yr  <- sdg_yr  |> filter(company == "coromandel")
co_maturity <- compute_maturity_index(co_ev_wide)

jsw_ev      <- ev      |> filter(company == "jswsteel")
jsw_ev_wide <- ev_wide |> filter(company == "jswsteel")
jsw_sdg_yr  <- sdg_yr  |> filter(company == "jswsteel")
jsw_maturity <- compute_maturity_index(jsw_ev_wide)
```

## Theoretical framework

Standard SDG disclosure analysis counts SDG mentions or scores disclosures on rubrics. This chapter extends that approach by treating SDG disclosure as a **relational network** — where SDGs are nodes connected to evidence types, implementation stages, and governance signals.

This allows us to examine not only *which* SDGs appear, but *how they are embedded* in operational, strategic, and measurable disclosure structures over time.

The core theoretical claim:

> *Firms transition through four stages of SDG disclosure maturity: rhetorical alignment → strategic commitment → operational implementation → governed, measured outcomes. This transition is visible not only in average scores but in the topological shift of the SDG-evidence network.*

---

## 4.1 SDG × Evidence Tag Interaction Map

### Full dataset (all years)

Nodes: SDGs and evidence tag types. **Edge thickness** = evidence count (breadth). **Edge colour** = average score (depth). An edge that is thick but pale = many items, but weakly evidenced. Thick and dark = genuinely operationalised.

::: {.panel-tabset}

#### Coromandel

```{r tag-network-full, fig.height=7}
g_tag_all_co <- build_sdg_tag_network(co_ev)
plot_bipartite_network(g_tag_all_co,
  title = "SDG × Evidence tag network — Coromandel all years")
```

#### JSW Steel

```{r tag-network-full-jsw, fig.height=7}
g_tag_all_jsw <- build_sdg_tag_network(jsw_ev)
plot_bipartite_network(g_tag_all_jsw,
  title = "SDG × Evidence tag network — JSW Steel all years")
```

:::

### Interactive version (hover to explore)

::: {.panel-tabset}

#### Coromandel

```{r tag-network-interactive}
plot_interactive_network(g_tag_all_co,
  title = "SDG × Evidence Tag Network — Coromandel")
```

#### JSW Steel

```{r tag-network-interactive-jsw}
plot_interactive_network(g_tag_all_jsw,
  title = "SDG × Evidence Tag Network — JSW Steel")
```

:::

### Period comparison: Annual reports vs Integrated reports

Has the network topology changed between reporting eras? For Coromandel this marks the 2022 shift to integrated reporting. For JSW Steel, 2020 falls in the pre-integrated era with 2022–2025 in the BRSR/integrated era.

::: {.panel-tabset}

#### Coromandel — Annual era (2016–2021)

```{r tag-net-annual, fig.height=6}
g_tag_pre_co <- build_sdg_tag_network(co_ev, filter_period = "Annual (2016–2021)")
plot_bipartite_network(g_tag_pre_co, title = "Coromandel — Annual reports era (2016–2021)")
```

#### Coromandel — Integrated era (2022–2025)

```{r tag-net-integrated, fig.height=6}
g_tag_post_co <- build_sdg_tag_network(co_ev, filter_period = "Integrated (2022–2025)")
plot_bipartite_network(g_tag_post_co, title = "Coromandel — Integrated reports era (2022–2025)")
```

#### JSW Steel — Pre-2022 (2020)

```{r tag-net-jsw-pre, fig.height=6}
g_tag_pre_jsw <- build_sdg_tag_network(jsw_ev, filter_period = "Annual (2016–2021)")
plot_bipartite_network(g_tag_pre_jsw, title = "JSW Steel — Pre-2022 era (2020)")
```

#### JSW Steel — 2022–2025

```{r tag-net-jsw-post, fig.height=6}
g_tag_post_jsw <- build_sdg_tag_network(jsw_ev, filter_period = "Integrated (2022–2025)")
plot_bipartite_network(g_tag_post_jsw, title = "JSW Steel — BRSR / Integrated era (2022–2025)")
```

:::

---

## 4.2 SDG × Implementation Stage Maturity Map

Which SDGs have escaped rhetoric (`mention_only`) and reached measurable evidence? The structure of this bipartite network shows maturity profiles at a glance.

::: {.panel-tabset}

#### Coromandel

```{r stage-network-full, fig.height=7}
g_stage_all_co <- build_sdg_stage_network(co_ev)
plot_bipartite_network(g_stage_all_co,
  title = "SDG × Implementation stage — Coromandel all years")
```

#### JSW Steel

```{r stage-network-full-jsw, fig.height=7}
g_stage_all_jsw <- build_sdg_stage_network(jsw_ev)
plot_bipartite_network(g_stage_all_jsw,
  title = "SDG × Implementation stage — JSW Steel all years")
```

:::

::: {.panel-tabset}

#### Coromandel — Pre-integrated (2016–2021)

```{r stage-net-pre, fig.height=6}
g_stage_pre <- build_sdg_stage_network(co_ev, filter_period = "Annual (2016–2021)")
plot_bipartite_network(g_stage_pre, title = "Coromandel — Stage network — Annual era")
```

#### Coromandel — Post-integrated (2022–2025)

```{r stage-net-post, fig.height=6}
g_stage_post <- build_sdg_stage_network(co_ev, filter_period = "Integrated (2022–2025)")
plot_bipartite_network(g_stage_post, title = "Coromandel — Stage network — Integrated era")
```

#### JSW Steel — Pre-2022 (2020)

```{r stage-net-jsw-pre, fig.height=6}
g_stage_pre_jsw <- build_sdg_stage_network(jsw_ev, filter_period = "Annual (2016–2021)")
plot_bipartite_network(g_stage_pre_jsw, title = "JSW Steel — Stage network — 2020")
```

#### JSW Steel — 2022–2025

```{r stage-net-jsw-post, fig.height=6}
g_stage_post_jsw <- build_sdg_stage_network(jsw_ev, filter_period = "Integrated (2022–2025)")
plot_bipartite_network(g_stage_post_jsw, title = "JSW Steel — Stage network — 2022–2025")
```

:::

---

## 4.3 SDG Co-occurrence Network

Which SDGs appear together in the same evidence item? Dense co-occurrence suggests integrated thinking; isolated SDGs may be tokenistic inclusions.

::: {.panel-tabset}

#### Coromandel

```{r cooccur-network, fig.height=6}
g_co_co <- build_sdg_cooccurrence_network(co_ev_wide)
if (!is.null(g_co_co)) {
  ggraph(g_co_co, layout = "fr") +
    geom_edge_link(aes(width = count, alpha = count), colour = "#19486A") +
    scale_edge_width(range = c(0.3, 3), name = "Co-occurrences") +
    scale_edge_alpha(range = c(0.2, 0.9), guide = "none") +
    geom_node_point(aes(colour = name), size = 8, show.legend = FALSE) +
    scale_colour_sdg() +
    geom_node_label(aes(label = name), size = 2.8, repel = TRUE,
                    label.size = 0, fill = alpha("white", 0.85)) +
    labs(title = "SDG co-occurrence network — Coromandel all years",
         subtitle = "Edge thickness = number of evidence items citing both SDGs") +
    theme_graph(base_family = "sans")
} else {
  cat("No multi-SDG evidence items found.")
}
```

#### JSW Steel

```{r cooccur-network-jsw, fig.height=6}
g_co_jsw <- build_sdg_cooccurrence_network(jsw_ev_wide)
if (!is.null(g_co_jsw)) {
  ggraph(g_co_jsw, layout = "fr") +
    geom_edge_link(aes(width = count, alpha = count), colour = "#FD9D24") +
    scale_edge_width(range = c(0.3, 3), name = "Co-occurrences") +
    scale_edge_alpha(range = c(0.2, 0.9), guide = "none") +
    geom_node_point(aes(colour = name), size = 8, show.legend = FALSE) +
    scale_colour_sdg() +
    geom_node_label(aes(label = name), size = 2.8, repel = TRUE,
                    label.size = 0, fill = alpha("white", 0.85)) +
    labs(title = "SDG co-occurrence network — JSW Steel all years",
         subtitle = "Edge thickness = number of evidence items citing both SDGs") +
    theme_graph(base_family = "sans")
} else {
  cat("No multi-SDG evidence items found.")
}
```

:::

---

## 4.4 Maturity Index — Longitudinal Analysis

### Year-by-year trajectory with components

```{r maturity-decomposed}
make_comp_data <- function(mat, label) {
  mat |>
    mutate(report_year = as.integer(report_year)) |>
    select(report_year,
           `Score component`   = avg_score,
           `Stage component`   = stage_weight_avg,
           `Quality component` = quality_rate) |>
    mutate(company = label)
}

comp_co  <- make_comp_data(co_maturity,  "Coromandel")
comp_jsw <- make_comp_data(jsw_maturity, "JSW Steel")

comp_colours <- c("Score component" = "#19486A", "Stage component" = "#3F7E44",
                  "Quality component" = "#FCC30B")
comp_names   <- c("Score component", "Stage component", "Quality component")
```

::: {.panel-tabset}

#### Coromandel

```{r maturity-decomposed-co}
p <- plot_ly()
for (cn in comp_names) {
  y_sym <- as.formula(paste0("~`", cn, "`"))
  p <- p |>
    add_trace(data = comp_co, x = ~report_year, y = y_sym,
              name = cn, type = "scatter", mode = "lines+markers",
              line   = list(color = comp_colours[[cn]], width = 2),
              marker = list(color = comp_colours[[cn]], size = 6))
}
p |> layout(
  title = "Maturity components — Coromandel",
  xaxis = list(title = "Report year", tickvals = comp_co$report_year),
  yaxis = list(title = "Component value [0–1]", range = c(0, 1),
               tickformat = ".0%"),
  shapes = list(list(
    type = "line", x0 = 2021.5, x1 = 2021.5, y0 = 0, y1 = 1,
    line = list(color = "grey50", dash = "dash", width = 1)
  )),
  annotations = list(list(
    x = 2021.7, y = 0.9, text = "Integrated<br>reporting",
    showarrow = FALSE, xanchor = "left", font = list(color = "grey40", size = 11)
  )),
  legend = list(orientation = "h")
)
```

#### JSW Steel

```{r maturity-decomposed-jsw}
p <- plot_ly()
for (cn in comp_names) {
  y_sym <- as.formula(paste0("~`", cn, "`"))
  p <- p |>
    add_trace(data = comp_jsw, x = ~report_year, y = y_sym,
              name = cn, type = "scatter", mode = "lines+markers",
              line   = list(color = comp_colours[[cn]], width = 2),
              marker = list(color = comp_colours[[cn]], size = 6))
}
p |> layout(
  title = "Maturity components — JSW Steel",
  xaxis = list(title = "Report year", tickvals = comp_jsw$report_year),
  yaxis = list(title = "Component value [0–1]", range = c(0, 1),
               tickformat = ".0%"),
  legend = list(orientation = "h")
)
```

:::

### Pre/post period comparison

::: {.panel-tabset}

#### Coromandel

```{r period-comparison}
compute_period_summary(co_ev_wide) |>
  select(
    Period         = period,
    `N items`      = n_items,
    `Avg score`    = avg_score,
    `% Measurable` = pct_measurable,
    `% Strong`     = pct_strong,
    `Quant rate`   = quant_rate,
    `Oversight rate` = oversight_rate
  ) |>
  mutate(across(where(is.numeric), ~round(.x, 2))) |>
  reactable(
    columns = list(
      Period = colDef(minWidth = 180),
      `% Measurable` = colDef(cell = function(v) scales::percent(v, accuracy = 1)),
      `% Strong`     = colDef(cell = function(v) scales::percent(v, accuracy = 1)),
      `Quant rate`   = colDef(cell = function(v) scales::percent(v, accuracy = 1)),
      `Oversight rate` = colDef(cell = function(v) scales::percent(v, accuracy = 1))
    ),
    striped = TRUE, highlight = TRUE
  )
```

#### JSW Steel

```{r period-comparison-jsw}
compute_period_summary(jsw_ev_wide) |>
  select(
    Period         = period,
    `N items`      = n_items,
    `Avg score`    = avg_score,
    `% Measurable` = pct_measurable,
    `% Strong`     = pct_strong,
    `Quant rate`   = quant_rate,
    `Oversight rate` = oversight_rate
  ) |>
  mutate(across(where(is.numeric), ~round(.x, 2))) |>
  reactable(
    columns = list(
      Period = colDef(minWidth = 180),
      `% Measurable` = colDef(cell = function(v) scales::percent(v, accuracy = 1)),
      `% Strong`     = colDef(cell = function(v) scales::percent(v, accuracy = 1)),
      `Quant rate`   = colDef(cell = function(v) scales::percent(v, accuracy = 1)),
      `Oversight rate` = colDef(cell = function(v) scales::percent(v, accuracy = 1))
    ),
    striped = TRUE, highlight = TRUE
  )
```

:::

### Segmented regression: did integrated reporting cause a structural break?

::: {.panel-tabset}

#### Coromandel

```{r segmented-regression}
reg_data <- co_maturity |>
  mutate(
    post      = as.integer(report_year >= 2022),
    time      = report_year - min(report_year),
    time_post = time * post
  )

if (nrow(reg_data) >= 5) {
  m <- lm(maturity_index ~ time + post + time_post, data = reg_data)

  reg_plot <- reg_data |>
    mutate(fitted = fitted(m),
           report_year = as.integer(report_year),
           period      = as.character(period),
           hover       = paste0(period, "<br>", report_year,
                                "<br>Maturity: ", scales::percent(maturity_index, 0.1)))

  period_colours <- c("Annual (2016–2021)" = "#FD9D24",
                      "Integrated (2022–2025)" = "#19486A")
  pre_d  <- reg_plot |> filter(post == 0)
  post_d <- reg_plot |> filter(post == 1)

  plot_ly() |>
    add_trace(data = pre_d, x = ~report_year, y = ~fitted,
              type = "scatter", mode = "lines",
              line = list(color = "#19486A", width = 2), showlegend = FALSE) |>
    add_trace(data = post_d, x = ~report_year, y = ~fitted,
              type = "scatter", mode = "lines",
              line = list(color = "#19486A", width = 2), showlegend = FALSE) |>
    add_trace(data = reg_plot, x = ~report_year, y = ~maturity_index,
              color = ~period, colors = period_colours,
              type = "scatter", mode = "markers",
              marker = list(size = 10), text = ~hover, hoverinfo = "text") |>
    layout(
      title = paste0(
        "Coromandel — Interrupted time series<br>",
        "<sub>Post-break slope change β₃ = ", round(coef(m)["time_post"], 4),
        " (n = ", nrow(reg_data), " years)</sub>"
      ),
      xaxis = list(title = "Report year", tickvals = reg_plot$report_year),
      yaxis = list(title = "Maturity index", range = c(0, 1), tickformat = ".0%"),
      shapes = list(list(
        type = "line", x0 = 2021.5, x1 = 2021.5, y0 = 0, y1 = 1,
        line = list(color = "grey50", dash = "dash", width = 1)
      )),
      legend = list(orientation = "h")
    )
} else {
  cat("Insufficient years for segmented regression (need ≥ 5 data points).")
}
```

#### JSW Steel

```{r segmented-regression-jsw}
reg_data_jsw <- jsw_maturity |>
  mutate(
    post      = as.integer(report_year >= 2022),
    time      = report_year - min(report_year),
    time_post = time * post
  )

if (nrow(reg_data_jsw) >= 5) {
  m_jsw <- lm(maturity_index ~ time + post + time_post, data = reg_data_jsw)

  reg_plot_jsw <- reg_data_jsw |>
    mutate(fitted = fitted(m_jsw),
           report_year = as.integer(report_year),
           period      = as.character(period),
           hover       = paste0(period, "<br>", report_year,
                                "<br>Maturity: ", scales::percent(maturity_index, 0.1)))

  period_colours <- c("Annual (2016–2021)" = "#FD9D24",
                      "Integrated (2022–2025)" = "#FD9D24")
  pre_d  <- reg_plot_jsw |> filter(post == 0)
  post_d <- reg_plot_jsw |> filter(post == 1)

  plot_ly() |>
    add_trace(data = pre_d, x = ~report_year, y = ~fitted,
              type = "scatter", mode = "lines",
              line = list(color = "#FD9D24", width = 2), showlegend = FALSE) |>
    add_trace(data = post_d, x = ~report_year, y = ~fitted,
              type = "scatter", mode = "lines",
              line = list(color = "#FD9D24", width = 2), showlegend = FALSE) |>
    add_trace(data = reg_plot_jsw, x = ~report_year, y = ~maturity_index,
              color = ~period, colors = period_colours,
              type = "scatter", mode = "markers",
              marker = list(size = 10), text = ~hover, hoverinfo = "text") |>
    layout(
      title = paste0(
        "JSW Steel — Interrupted time series<br>",
        "<sub>Post-break slope change β₃ = ", round(coef(m_jsw)["time_post"], 4),
        " (n = ", nrow(reg_data_jsw), " years)</sub>"
      ),
      xaxis = list(title = "Report year", tickvals = reg_plot_jsw$report_year),
      yaxis = list(title = "Maturity index", range = c(0, 1), tickformat = ".0%"),
      shapes = list(list(
        type = "line", x0 = 2021.5, x1 = 2021.5, y0 = 0, y1 = 1,
        line = list(color = "grey50", dash = "dash", width = 1)
      )),
      legend = list(orientation = "h")
    )
} else {
  cat("Insufficient years for segmented regression (need ≥ 5 data points).")
}
```

:::

::: {.callout-warning}
**Statistical caution:** With fewer than 15 annual observations per company, segmented regression is illustrative rather than inferential. The coefficient direction and magnitude are meaningful; p-values should not be over-interpreted.
:::

---

## 4.5 Anomaly Detection

### High-confidence items that scored weak

Items where the model was confident but the deterministic rubric scored low. These warrant manual review — either the rubric is too strict, or the model over-estimated evidence quality.

::: {.panel-tabset}

#### Coromandel

```{r anomaly-high-conf-weak}
co_ev_wide |>
  filter(confidence >= 0.8, computed_strength == "weak") |>
  arrange(desc(confidence)) |>
  select(Year = report_year, Page = page_number, Score = computed_score,
         Confidence = confidence, Stage = implementation_stage,
         SDGs = candidate_sdgs, Summary = evidence_summary) |>
  mutate(SDGs = map_chr(SDGs, paste, collapse = ", ")) |>
  reactable(striped = TRUE, highlight = TRUE, searchable = TRUE,
            defaultPageSize = 8)
```

#### JSW Steel

```{r anomaly-high-conf-weak-jsw}
jsw_ev_wide |>
  filter(confidence >= 0.8, computed_strength == "weak") |>
  arrange(desc(confidence)) |>
  select(Year = report_year, Page = page_number, Score = computed_score,
         Confidence = confidence, Stage = implementation_stage,
         SDGs = candidate_sdgs, Summary = evidence_summary) |>
  mutate(SDGs = map_chr(SDGs, paste, collapse = ", ")) |>
  reactable(striped = TRUE, highlight = TRUE, searchable = TRUE,
            defaultPageSize = 8)
```

:::

### SDG score drops year-over-year (retreat signals)

SDG-years where the average score dropped by more than 1 point from the previous year.

::: {.panel-tabset}

#### Coromandel

```{r score-drops}
drops_co <- co_sdg_yr |>
  arrange(sdg, report_year) |>
  group_by(sdg) |>
  mutate(prev_score = lag(average_score), delta = average_score - prev_score) |>
  filter(!is.na(delta), delta < -1) |>
  ungroup() |>
  select(SDG = sdg, Year = report_year,
         `Previous score` = prev_score,
         `Current score`  = average_score,
         `Drop` = delta) |>
  arrange(Drop)

if (nrow(drops_co) > 0) {
  reactable(drops_co, striped = TRUE, highlight = TRUE,
            columns = list(Drop = colDef(
              style = function(v) list(color = "#E5243B", fontWeight = "bold")
            )))
} else {
  cat("No score drops > 1 point detected.")
}
```

#### JSW Steel

```{r score-drops-jsw}
drops_jsw <- jsw_sdg_yr |>
  arrange(sdg, report_year) |>
  group_by(sdg) |>
  mutate(prev_score = lag(average_score), delta = average_score - prev_score) |>
  filter(!is.na(delta), delta < -1) |>
  ungroup() |>
  select(SDG = sdg, Year = report_year,
         `Previous score` = prev_score,
         `Current score`  = average_score,
         `Drop` = delta) |>
  arrange(Drop)

if (nrow(drops_jsw) > 0) {
  reactable(drops_jsw, striped = TRUE, highlight = TRUE,
            columns = list(Drop = colDef(
              style = function(v) list(color = "#E5243B", fontWeight = "bold")
            )))
} else {
  cat("No score drops > 1 point detected.")
}
```

:::

---

## 4.6 Difference Network — What Changed?

Edge weight change from pre-2022 era → post-2022 era. **Green edges** = strengthened connections. **Red edges** = weakened.

::: {.panel-tabset}

#### Coromandel

```{r difference-network, fig.height=7}
make_diff_network <- function(company_ev, title_label) {
  edges_pre <- company_ev |>
    filter(period == "Annual (2016–2021)") |>
    unnest(evidence_tags) |> rename(tag = evidence_tags) |>
    group_by(sdg, tag) |>
    summarise(score_pre = mean(computed_score, na.rm = TRUE), .groups = "drop") |>
    mutate(sdg = as.character(sdg))

  edges_post <- company_ev |>
    filter(period == "Integrated (2022–2025)") |>
    unnest(evidence_tags) |> rename(tag = evidence_tags) |>
    group_by(sdg, tag) |>
    summarise(score_post = mean(computed_score, na.rm = TRUE), .groups = "drop") |>
    mutate(sdg = as.character(sdg))

  diff_edges <- full_join(edges_pre, edges_post, by = c("sdg", "tag")) |>
    mutate(
      score_pre  = replace_na(score_pre,  0),
      score_post = replace_na(score_post, 0),
      delta      = score_post - score_pre,
      direction  = if_else(delta >= 0, "Strengthened", "Weakened")
    ) |>
    filter(abs(delta) > 0.5)

  if (nrow(diff_edges) == 0) {
    cat("No meaningful score changes detected between periods.")
    return(invisible(NULL))
  }

  all_nodes <- union(diff_edges$sdg, diff_edges$tag)
  node_df   <- tibble(
    name      = all_nodes,
    node_type = if_else(str_starts(name, "SDG"), "SDG", "Tag"),
    type      = !str_starts(name, "SDG")
  )

  g_diff <- tbl_graph(
    nodes = node_df,
    edges = diff_edges |> rename(from = sdg, to = tag),
    directed = FALSE
  )

  ggraph(g_diff, layout = "bipartite") +
    geom_edge_link(aes(colour = direction, width = abs(delta), alpha = abs(delta)),
                   show.legend = TRUE) +
    scale_edge_colour_manual(values = c("Strengthened" = "#3F7E44", "Weakened" = "#E5243B"),
                             name = "Change direction") +
    scale_edge_width(range = c(0.5, 4), name = "|Δ score|", guide = "none") +
    scale_edge_alpha(range = c(0.4, 1), guide = "none") +
    geom_node_point(aes(colour = node_type), size = 5) +
    scale_colour_manual(values = c("SDG" = "#19486A", "Tag" = "#666666"),
                        name = "Node type") +
    geom_node_label(aes(label = name), repel = TRUE, size = 3,
                    label.size = 0, fill = alpha("white", 0.8)) +
    labs(title    = paste0(title_label, " — Difference network"),
         subtitle = "Green = score increased · Red = score decreased · Width = magnitude") +
    theme_graph(base_family = "sans") +
    theme(legend.position = "right")
}

make_diff_network(co_ev, "Coromandel: Annual → Integrated era")
```

#### JSW Steel

```{r difference-network-jsw, fig.height=7}
make_diff_network(jsw_ev, "JSW Steel: Pre-2022 → 2022–2025")
```

:::
