---
title: "JSW Steel"
subtitle: "SDG Disclosure 2020–2025"
---

```{r setup, include=FALSE}
library(here); library(reactable); library(plotly); library(gt)
source(here("R", "load_evidence.R"))
source(here("R", "plot_themes.R"))
source(here("R", "scoring_helpers.R"))
source(here("R", "download_helpers.R"))

# Filter to JSW Steel only
co_ev      <- ev      |> filter(company == "jswsteel")
co_ev_wide <- ev_wide |> filter(company == "jswsteel")
co_meta    <- run_meta|> filter(company == "jswsteel")
co_sdg_yr  <- sdg_yr  |> filter(company == "jswsteel")
co_maturity <- compute_maturity_index(co_ev_wide)
```

## SDG Portfolio Heatmap

The single most informative view: which SDGs appear, in which years, and how deeply?
**Colour intensity** = average computed score (0–13). **Cell number** = evidence count.

```{r sdg-heatmap}
heat_data <- co_sdg_yr |>
  mutate(sdg = fct_reorder(as.character(sdg), sdg_num))

p <- heat_data |>
  ggplot(aes(x = report_year, y = sdg,
             fill = average_score, text = paste0(
               sdg, " · ", report_year,
               "\nEvidence: ", evidence_count,
               "\nAvg score: ", round(average_score, 2),
               "\n", implementation_profile
             ))) +
  geom_tile(colour = "white", linewidth = 0.5) +
  geom_text(aes(label = evidence_count), size = 2.8,
            colour = "white", fontface = "bold") +
  scale_fill_gradient2(
    low = "#D9EAD3", mid = "#4C9F38", high = "#19486A",
    midpoint = 5, na.value = "grey92",
    name = "Avg score\n(0–13)"
  ) +
  scale_x_continuous(breaks = unique(heat_data$report_year)) +
  labs(
    title    = "JSW Steel SDG disclosure portfolio 2020–2025",
    subtitle = "Cell colour = average evidence score · Number = evidence count",
    x = "Report year", y = NULL
  ) +
  theme_sdg() +
  theme(
    axis.text.y   = element_text(size = 9),
    panel.grid    = element_blank()
  )

ggplotly(p, tooltip = "text") |>
  layout(yaxis = list(autorange = "reversed"))
```

---

## Disclosure Volume Trends

```{r volume-trends}
yr  <- as.integer(unlist(co_meta$report_year))
nv  <- as.integer(unlist(co_meta$n_valid))
nr  <- as.integer(unlist(co_meta$n_rejected))
rr  <- as.numeric(unlist(co_meta$rejection_rate))

plot_ly() |>
  add_trace(x = yr, y = nv, name = "Valid",
            type = "scatter", mode = "lines+markers",
            line = list(color = "#3F7E44", width = 2),
            marker = list(color = "#3F7E44", size = 7)) |>
  add_trace(x = yr, y = nr, name = "Rejected",
            type = "scatter", mode = "lines+markers",
            line = list(color = "#E5243B", width = 2, dash = "dash"),
            marker = list(color = "#E5243B", size = 7)) |>
  layout(title = "Evidence items per year",
         xaxis = list(title = "Report year", tickvals = yr),
         yaxis = list(title = "Count"),
         legend = list(orientation = "h"))
```

```{r rejection-rate}
mean_rr <- mean(rr, na.rm = TRUE)
plot_ly(x = yr, y = rr, type = "bar",
        marker = list(color = "#E5243B", opacity = 0.7)) |>
  layout(title = "Rejection rate per year",
         xaxis = list(title = "Report year", tickvals = yr),
         yaxis = list(title = "Rejection rate", tickformat = ".0%"),
         shapes = list(list(
           type = "line", x0 = 0, x1 = 1, xref = "paper",
           y0 = mean_rr, y1 = mean_rr,
           line = list(color = "grey40", dash = "dash", width = 1.5)
         )))
```

---

## Maturity Trajectory

### Implementation stage composition over time

The key question: is `mention_only` shrinking and `implemented_with_measurable_evidence` growing?

```{r stage-stacked}
stage_data <- co_ev_wide |>
  count(report_year, implementation_stage) |>
  group_by(report_year) |>
  mutate(pct = n / sum(n)) |>
  ungroup()

p <- stage_data |>
  ggplot(aes(x = report_year, y = pct, fill = implementation_stage,
             text = paste0(STAGE_LABELS[as.character(implementation_stage)],
                           "\n", scales::percent(pct, accuracy = 1)))) +
  geom_col(width = 0.7, position = "stack") +
  scale_fill_stage() +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = unique(co_ev_wide$report_year)) +
  labs(
    title    = "Implementation stage composition per year",
    subtitle = "Maturing disclosure: red tones shrink, dark tones grow",
    x = "Report year", y = "Proportion of evidence items",
    fill = "Stage"
  ) +
  theme_sdg()

ggplotly(p, tooltip = "text")
```

### Maturity index over time

```{r maturity-index}
mat_df <- co_maturity |>
  mutate(
    report_year    = as.integer(report_year),
    maturity_index = as.numeric(maturity_index),
    period         = as.character(period),
    hover          = paste0(period, "<br>Year: ", report_year,
                            "<br>Maturity: ", scales::percent(maturity_index, 0.1))
  )
period_colours <- c("Annual (2016–2021)" = "#FD9D24", "Integrated (2022–2025)" = "#19486A")

plot_ly(mat_df, x = ~report_year) |>
  add_lines(y = ~maturity_index,
            line = list(color = "#19486A", width = 2),
            showlegend = FALSE, hoverinfo = "none") |>
  add_markers(y = ~maturity_index,
              color = ~period, colors = period_colours,
              marker = list(size = 10),
              text = ~hover, hoverinfo = "text") |>
  layout(
    title = "SDG disclosure maturity index — JSW Steel 2020–2025",
    xaxis = list(title = "Report year", tickvals = ~report_year),
    yaxis = list(title = "Maturity index [0–1]", range = c(0, 1),
                 tickformat = ".0%"),
    legend = list(orientation = "h")
  )
```

---

## Evidence Quality Dimensions

```{r quality-dims}
quality_yr <- co_ev_wide |>
  group_by(report_year) |>
  summarise(
    quant_rate     = mean(quantitative_support, na.rm = TRUE),
    oversight_rate = mean(oversight_support,    na.rm = TRUE),
    .groups = "drop"
  ) |>
  mutate(report_year = as.integer(report_year))

plot_ly(quality_yr, x = ~report_year) |>
  add_trace(y = ~quant_rate, name = "Quantitative support",
            type = "scatter", mode = "lines+markers",
            line = list(color = "#3F7E44", width = 2),
            marker = list(color = "#3F7E44", size = 7)) |>
  add_trace(y = ~oversight_rate, name = "Oversight support",
            type = "scatter", mode = "lines+markers",
            line = list(color = "#0A97D9", width = 2),
            marker = list(color = "#0A97D9", size = 7)) |>
  layout(
    title = "Evidence quality rates per year",
    xaxis = list(title = "Report year", tickvals = ~report_year),
    yaxis = list(title = "Rate", range = c(0, 1), tickformat = ".0%"),
    legend = list(orientation = "h")
  )
```

::: {.callout-note}
These two dimensions are the hardest signals to fake. A claim that passes both — it has a number **and** a named governance body — is the strongest kind of SDG evidence the pipeline can extract.
:::

---

## SDG Deep Dives

### Evidence count and average score per SDG (all years combined)

```{r sdg-summary}
sdg_totals <- co_ev |>
  group_by(sdg) |>
  summarise(
    n          = n(),
    avg_score  = round(mean(computed_score, na.rm = TRUE), 2),
    quant_rate = scales::percent(mean(quantitative_support, na.rm = TRUE), accuracy = 1),
    pct_strong = scales::percent(mean(computed_strength == "strong", na.rm = TRUE), accuracy = 1),
    years      = paste(sort(unique(report_year)), collapse = ", "),
    .groups    = "drop"
  ) |>
  arrange(desc(avg_score))

make_download_bar(sdg_totals, "jswsteel_sdg_summary")
reactable(
  sdg_totals,
  columns = list(
    sdg        = colDef(name = "SDG", maxWidth = 80),
    n          = colDef(name = "Evidence items", maxWidth = 130, align = "center"),
    avg_score  = colDef(name = "Avg score", maxWidth = 100, align = "center"),
    quant_rate = colDef(name = "Quant. support", maxWidth = 130, align = "center"),
    pct_strong = colDef(name = "% Strong", maxWidth = 100, align = "center"),
    years      = colDef(name = "Years present", minWidth = 150)
  ),
  striped = TRUE, highlight = TRUE, searchable = TRUE,
  defaultSortOrder = "desc",
  defaultSorted = "avg_score"
)
```

### Top evidence items (strongest, with page citations)

```{r top-evidence}
top_ev <- co_ev_wide |>
  arrange(desc(computed_score), desc(confidence)) |>
  slice_head(n = 30) |>
  select(
    Year     = report_year,
    Page     = page_number,
    Score    = computed_score,
    Strength = computed_strength,
    Stage    = implementation_stage,
    SDGs     = candidate_sdgs,
    Tags     = evidence_tags,
    Summary  = evidence_summary,
    Text     = evidence_text
  ) |>
  mutate(
    SDGs = map_chr(SDGs, paste, collapse = ", "),
    Tags = map_chr(Tags, paste, collapse = ", "),
    Stage = recode(as.character(Stage),
      mention_only                         = "Mention",
      planned_action                       = "Planned",
      implementation_in_progress           = "In progress",
      implemented_with_measurable_evidence = "Measurable"
    )
  )

make_download_bar(top_ev, "jswsteel_top_evidence")
reactable(
  top_ev,
  columns = list(
    Year     = colDef(maxWidth = 60,  align = "center"),
    Page     = colDef(maxWidth = 55,  align = "center"),
    Score    = colDef(maxWidth = 60,  align = "center",
                      style = function(v) list(fontWeight = "bold", color = "#19486A")),
    Strength = colDef(maxWidth = 90,  align = "center"),
    Stage    = colDef(maxWidth = 100),
    SDGs     = colDef(maxWidth = 120),
    Tags     = colDef(maxWidth = 160),
    Summary  = colDef(minWidth = 200),
    Text     = colDef(minWidth = 250, show = FALSE)
  ),
  details = function(index) {
    htmltools::div(
      style = "padding: 8px 16px; background: #f8f9fa; border-left: 3px solid #19486A;",
      htmltools::strong("Verbatim text: "),
      top_ev$Text[index]
    )
  },
  striped = TRUE, highlight = TRUE, searchable = TRUE,
  defaultPageSize = 10
)
```

---

## All Evidence — Full Searchable Table

```{r full-table}
all_ev <- co_ev_wide |>
  arrange(report_year, desc(computed_score)) |>
  transmute(
    Year     = report_year,
    Page     = page_number,
    Section  = section_heading,
    Score    = computed_score,
    Strength = as.character(computed_strength),
    Stage    = recode(as.character(implementation_stage),
      mention_only                         = "Mention only",
      planned_action                       = "Planned",
      implementation_in_progress           = "In progress",
      implemented_with_measurable_evidence = "Measurable"
    ),
    SDGs     = map_chr(candidate_sdgs, paste, collapse = ", "),
    Tags     = map_chr(evidence_tags,  paste, collapse = ", "),
    Quant    = if_else(quantitative_support, "✓", ""),
    Oversight= if_else(oversight_support, "✓", ""),
    Summary  = evidence_summary,
    Text     = evidence_text
  )

make_download_bar(all_ev, "jswsteel_all_evidence")
reactable(
  all_ev,
  columns = list(
    Year     = colDef(maxWidth = 60,  align = "center", filterable = TRUE),
    Page     = colDef(maxWidth = 55,  align = "center"),
    Section  = colDef(maxWidth = 160, show = FALSE),
    Score    = colDef(maxWidth = 60,  align = "center"),
    Strength = colDef(maxWidth = 90,  align = "center", filterable = TRUE),
    Stage    = colDef(maxWidth = 110, filterable = TRUE),
    SDGs     = colDef(maxWidth = 120, filterable = TRUE),
    Tags     = colDef(maxWidth = 160),
    Quant    = colDef(maxWidth = 60,  align = "center", name = "Quant"),
    Oversight= colDef(maxWidth = 75,  align = "center", name = "Govern"),
    Summary  = colDef(minWidth = 200),
    Text     = colDef(show = FALSE)
  ),
  details = function(index) {
    htmltools::div(
      style = "padding: 8px 16px; background: #f8f9fa; border-left: 3px solid #19486A;",
      htmltools::strong("Section: "), all_ev$Section[index], htmltools::br(),
      htmltools::strong("Verbatim: "), all_ev$Text[index]
    )
  },
  filterable = TRUE, searchable = TRUE,
  striped = TRUE, highlight = TRUE, compact = TRUE,
  defaultPageSize = 15
)
```
