---
title: "SDG Disclosure Observatory"
subtitle: "About this research tool"
---

```{r setup, include=FALSE}
library(here)
source(here("R", "load_evidence.R"))
source(here("R", "plot_themes.R"))
source(here("R", "scoring_helpers.R"))
```

## What this tool does

This observatory measures how companies disclose alignment with the UN Sustainable Development Goals (SDGs) — tracking **disclosure maturity** across years, report types, and peer companies. The current dataset covers **Coromandel** (2016–2025, 10 reports) and **JSW Steel** (2020–2025, 5 reports).

The underlying data is produced by a local-first Python pipeline that:

1. Extracts text from PDF reports page-by-page
2. Retrieves SDG-relevant passages using hybrid semantic + keyword retrieval
3. Extracts structured evidence using a local LLM (Gemma2 via Ollama)
4. Validates every evidence item against deterministic rules
5. Scores evidence using a documented rubric — no model-assigned strength labels

This tool does **not** summarise what companies claim. It surfaces **auditable text evidence** and measures **disclosure maturity** — the structural difference between rhetorical SDG alignment and governed, quantified, operational implementation.

---

## How to navigate

| Chapter | What it answers |
|---------|----------------|
| **1 · Methods** | How is evidence extracted, validated, and scored? |
| **2 · Coromandel** | What does Coromandel's full SDG disclosure trajectory look like? |
| **3 · JSW Steel** | What does JSW Steel's SDG disclosure profile look like? |
| **4 · Comparison** | How do the two companies compare on maturity and SDG coverage? |
| **5 · Theory** | Is there a measurable transition from rhetoric to implementation? |
| **6 · Reports Library** | Browse the full pipeline report for any company × year. |

---

## Dataset at a glance

```{r summary-cards}
library(gt)

run_meta |>
  group_by(Company = stringr::str_to_title(company)) |>
  summarise(
    Reports  = n(),
    Valid    = sum(n_valid),
    Rejected = sum(n_rejected),
    `SDGs covered` = n_distinct(ev$sdg[ev$company == unique(company)]),
    .groups = "drop"
  ) |>
  bind_rows(
    run_meta |>
      summarise(
        Company  = "Total",
        Reports  = n(),
        Valid    = sum(n_valid),
        Rejected = sum(n_rejected),
        `SDGs covered` = n_distinct(ev$sdg)
      )
  ) |>
  gt() |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(rows = Company == "Total")
  ) |>
  tab_style(
    style = list(cell_fill(color = "#f0f4f8"), cell_text(weight = "bold")),
    locations = cells_body(rows = Company == "Total")
  ) |>
  tab_options(table.border.top.style = "none",
              table.border.bottom.style = "none")
```

---

## Evidence per year

```{r yearly-bar}
library(plotly)

company_colours <- c("Coromandel" = "#19486A", "Jswsteel" = "#FD9D24")

p <- run_meta |>
  arrange(report_year) |>
  mutate(Company = stringr::str_to_title(company)) |>
  ggplot(aes(x = report_year, y = n_valid, fill = Company,
             text = paste0(Company, " ", report_year,
                           "\nValid: ", n_valid,
                           "\nRejected: ", n_rejected))) +
  geom_col(position = "dodge", width = 0.7) +
  scale_fill_manual(values = company_colours, name = NULL) +
  scale_x_continuous(breaks = unique(run_meta$report_year)) +
  labs(title = "Valid evidence items per report year",
       x = "Report year", y = "Valid evidence items") +
  theme_sdg()

ggplotly(p, tooltip = "text") |>
  layout(hovermode = "x unified", legend = list(orientation = "h"))
```

::: {.callout-note}
Rejected items failed one or more deterministic validation rules (e.g. a `measured_outcome` tag without quantitative support). They are stored separately and reviewed in Chapter 1.
:::

---

::: {.callout-note collapse="true"}
## Developer notes — rendering this book

From the `analysis/` directory:

```bash
quarto render          # full build → _book/index.html
quarto preview         # live preview in browser
```

Required R packages: `tidyverse`, `jsonlite`, `fs`, `here`, `gt`, `plotly`,
`reactable`, `ggraph`, `tidygraph`, `igraph`, `visNetwork`, `scales`, `commonmark`.
:::
